Scaffolder - Software for Microbial Genome Scaffolding.

### 2011-01-28 text/src/article.tex
Final results section discussing scaffolder

Pros
  * Do one thing and do it well
  * If your data structures are good enough, the algorithm to manipulate them should be trivial."

  * Reproducable steps in building a scaffold
  * Extensive documentation. Should be easy to use as possible.
  * Scaffold file allows meaningful construction of a scaffold
  * See of each sequence in building final draft genome
  * Keeping genome sequence in a scaffold file means it is simpler to edit after the fact.
  * Versionable plain text. Easy to store and see diffs
  * Common format for scaffold file means it can be easily manipulated programmatically.
  * Command line interface for using as is
  * Ruby API allowing more complex manipulation of the scaffold
  * Simple to install.  Automatically installed. No manual installation.

@@

Text for this section \ldots

>>>>

The main aims of scaffolder are two fold. The first is usuability and the second is reproducibility.

\subsubsection{Simple to use}

Scaffolder is designed to be as simple to use as possible. Assuming the
existence of Ruby and RubyGems, scaffolder can be installed with a single
command. Scaffolder uses a minimal and compact syntax to described the
scaffold. This syntax is simple to construct and edit whilst being succint and
readable in describing how the scaffold was constructed. Scaffolder provides
extensive documentation both for the command line tools and for the Scaffolder
Ruby API.

\subsubsection{Reproducible genome construction}

Constructing a genome sequence using a plain text scaffold file means the same
sequence is always output for the same file. The sequence produced from
manually joining separate contigs in a text editor can not be reliably
reproduced. Constructing the scaffold in a plain text file means that the
sequence is reproducible. Furthermore the source of each region in final
sequence can be identified. The scaffold file provides a readable record of
how the sequence was constructed. The scaffold file also means the scaffold is
easer to edit once already constructed. Much more difficult to do when working
on the sequence alone. The YAML text format is also much easier to compare
differences using standard diff commands. This makes scaffold files much more
simple to store in version control and to see the stages in the construction
of the genome sequence.

@@

  * Do one thing and do it well
  * If your data structures are good enough, the algorithm to manipulate them should be trivial."
